---
title: "MovePackage"
author: "Jeff Grayum"
date: "5/17/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

loading libraries
```{r}
library(tidyverse)
library(tidytuesdayR)
install.packages("move")
library(move)
```

Link to example: https://cran.r-project.org/web/packages/move/move.pdf

-contains functions to access movement data stored in movebank
-addresses ecological questions regarding movement

Creating Move objects
-move: create an object containing one animal track
-moveStack: create an object containing multiple move objects
-getMovebankData: creates a move or moveStack object with data from moveBank

Calculation of the utilization distribution
-brownian.bridge.dyn: calculates the occurrence distribution 
-getVolumeUD: calculates Utilization distribution

Accessing Values
-bbox: bounding box of Move* object
-coordinates: track-coordinates of a Move* object
-extent: extent of Move* object
-namesIndiv: names of a Move* object
-n.locs:  the number of locations of a Move* object.
-projection: the projection method of a Move* object or raster
-timeLag: the time lags between locations of a Move* object
-timeStamps: track time stamps of a Move* object

Plotting
-plot: plots utilization distribution or the track
-image: plots the UD fitted to a window
-contour: adds the contours of UD to a plot

Methods
-contour signature(object = ".UD"): adds a contour line to a plot, also for .UDStack
-emd signature(object = ".UD"): quantifies similarity between utilization distributions, also for
.UDStack
-getVolumeUD signature(object = ".UD"): modifies the .UD/.UDStack raster
-outerProbability signature(object = ".UD"): calculates the animal occurrence probabilities at the border of the raster (only for .UD class)
-plot signature(object = ".UD"): plots the raster from a .UD/.UDStack object with re-size in- sensitive proportions
-raster2contour signature(object = ".UD"): converts a raster to contour lines, also for .UD- Stack
-show signature(object = ".UD"): displays summary the .UD/.UDStack object
-summary signature(object=".UD"):summarizestheinformationoftherasterfroma.UD/.UDStack
object
-subset signature(object = ".UD"): subsets the .UD/.UDStack object
-split signature(object = ".UDStack"): splits a .UDStack into a list of .UD objects

##This page seems like great resource, might not be much value in going through it now.



-
